An Open Platform for Managing Short Programming Exercises

### 2013-06-22 paper/paper.tex
cite AGPL
more small edits
editing exercises section, add some refs

CloudCoder is an open platform for managing short programming
exercises.
Each exercise can be solved with one method or one short
program, and could take only a few minutes to solve, or could require
or an hour or two.  The system is not designed to support longer
programming assignments, such as those found at the {\em Nifty
Assignments} session at SIGCSE\cite{Parlante:2013:NA:2445196.2445356}.

@@

CloudCoder is available under the GNU Affero open-source license.
Binary distributions are available through our website (\url{http://cloudcoder.org}),
and the code is available on Github:

\vspace*{3mm} 
\url{https://github.com/cloudcoderdotorg/CloudCoder}
\vspace*{3mm}

@@

Writing good homework exercises is difficult and
time-consuming, and even the best textbooks are limited in the
number and quality of practice exercises they can provide, to say
nothing of a textbook's inability to provide timely feedback to
students.
Sharing exercises between faculty members is a much
more efficient way to increase the number and quality of exercises at
our disposal.

Faculty who use CloudCoder can write their own exercises using our in-browser
authoring tools, or can import exercises written by other faculty
from a central repository at:

\vspace*{3mm} 
\url{https://cloudcoder.org/repo}
\vspace*{3mm}

Currently we have over 50 Java and 60 C/C++ exercises authored by 5
different users.  By default,
any new exercises written by faculty will be shared to the 
central repository under a permissive Creative Commons license (BY-SA)
that allows redistribution provided that the author is credited and
redistribution is under the same license.  
(Note that the repository shows the exercise description, but not the
test cases or the solution, so an unscrupulous student cannot dig through the
repository for solutions.  Importing exercises requires an account at
the repository, which can be used to discourage this sort of
undesirable behavior.).

CloudCoder supports two types of exercises:  {\em method} or {\em function-based}
exercises, and {\em whole-program} exercises.  Function based exercises look
a lot like Codingbat exercises:  Students are given a description of
what the method should do, and a couple of example input/output pairs
similar to a unit test.  Writing a new function-based exercise
requires a description, some ``starter code'' (typically the method
header, although exercises can provide as much or as little code as
desired), and a series of inputs and their corresponding outputs.
Test-cases can be marked as ``secret'' so that students don't see their
outputs to discourage students from writing a special case to
recognize each input.

On the other hand, whole-program exercises
have a description, but read inputs from
standard-in and write to standard-out.  CloudCoder uses a
simplified regular expression language to check student outputs for
correctness.

@@

We run Java code relatively securely under a Security Manager, and 
use Jython and JRuby to compile Python and Ruby to Java
bytecode, which we also run in a Security-Managed sandbox.  We
currently support C/C++ less securely, although 
recent work by Malan\cite{Malan:2013:CSS:2445196.2445242} on a
``sandbox'' for running untrusted student code can be leveraged to improve our security.

>>>>

CloudCoder is an open platform for managing short programming
exercises.
Each exercise can be solved with one method or one short
program, and could take only a few minutes to solve, or could require
or an hour or two.  The system is not designed to support longer
programming assignments, such as those found at the {\em Nifty
Assignments} session at SIGCSE\cite{Parlante:2013:NA:2445196.2445356}.
Instead, they are intended to be used as self-test exercises,
practice problems, in-class lab activities, quiz problems, etc.

@@

CloudCoder is available under the GNU Affero General Public License\cite{AGPL}.
Binary distributions are available through our website (\url{http://cloudcoder.org}),
and the code is available on Github:
\begin{quote}
\url{https://github.com/cloudcoderdotorg/CloudCoder}
\end{quote}

@@

%Writing good homework exercises is difficult and
%time-consuming, and even the best textbooks are limited in the
%number and quality of practice exercises they can provide, to say
%nothing of a textbook's inability to provide timely feedback to
%students.
%Sharing exercises between faculty members is a much
%more efficient way to increase the number and quality of exercises at
%our disposal.
Writing a good programming exercise is challenging.
The instructions must be clear and concise.  The tests must
include easy inputs as well as more difficult corner cases.
If possible, tests should be constructed in a way that
allows a partially-correct solution to pass at least some
tests.  And, a good exercise should focus on a specific concept
or language construct.

%Faculty who use CloudCoder can write their own exercises using our in-browser
%authoring tools, or can import exercises written by other faculty
%from a central repository at:

Although instructors who use CloudCoder
could choose to write from scratch all of the exercises they assign,
our goal is to build a repository of good exercises
written by many users at many institutions, made available under
permissive licenses such as Creative Commons BY-SA\cite{CC-BY-SA}.
Once published to the repository, an exercise is available
for anyone who wishes to use it.
The exercise repository is available at the URL
\begin{quote}
\url{https://cloudcoder.org/repo}
\end{quote}
%
At the time of writing (June 2013) the exercise repository contains about 50 Java and
60 C/C++ exercises authored by 5 different users.  As more institutions
start to use CloudCoder, we expect the number of exercises to increase.
%By default,
%any new exercises written by faculty will be shared to the 
%central repository under a permissive Creative Commons license (BY-SA)
%that allows redistribution provided that the author is credited and
%redistribution is under the same license.  
%(Note that the repository shows the exercise description, but not the
%test cases or the solution, so an unscrupulous student cannot dig through the
%repository for solutions.  Importing exercises requires an account at
%the repository, which can be used to discourage this sort of
%undesirable behavior.)

CloudCoder supports two types of exercises:  {\em method} or {\em function-based}
exercises, and {\em whole-program} exercises.  Function based exercises are
very similar to CodingBat exercises: the student is required to write
a function/method that takes some number of parameter values,
does a computation, and returns a result value.
Students are given a description of
what the method should do, and a couple of example inputs with
expected results.  Writing a new function-based exercise
requires a description, some skeleton code (typically the method
header, although exercises can provide as much or as little code as
desired), and a series of inputs and their corresponding expected results.
Test cases can be marked as ``secret'' so that students don't see their
outputs, to discourage students from writing a special case to
recognize each input.

Whole-program exercises read input data from
the standard input stream, perform a computation, and write output to the standard output stream.
Expected output is checked by matching a regular expression against the
program's standard output stream.
Whole-program exercises are useful for two main reasons.  First,
they can be assigned early in the course, before functions/methods
have been introduced.  Second, they give the exercise author a
way of checking expected output that is more powerful than matching a return
value against a literal.  The main disadvantage is devising a
regular expression that is precise enough to distinguish correct output
from incorrect output, but forgiving enough to account for minor deviations
in whitespace, capitalization, and formatting of output.

@@

We run Java code relatively securely under a Security Manager, and 
use Jython\cite{jython} and JRuby\cite{jruby} to compile Python and Ruby to Java
bytecode, which we also run in a Security-Managed sandbox.  We
currently support C/C++ less securely, although 
we hope to take advantage of a better sandboxing mechanism
in the near future, possibly based on the work of
David Malan\cite{Malan:2013:CSS:2445196.2445242} for Harvard's
online CS50 course.
